---
# title: "Organizing team"
knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
---
```{css echo=FALSE}
.card-header-chairs{
  background-color: #FDC08666;
  font-weight: bold;
}
.card-header-team{
  background-color: #BEAED47A;
  font-weight: bold;
}

.card-header-comite{
  background-color: #B5D4EB;
  font-weight: bold;
}
.cards-display{
  display: grid;
}

.bslib-card {
  margin-bottom: 5px;
}
```


```{r}
source(here::here("R/functions-team.R"))
# update_info_team()
# team <- get_info_team()
# readr::write_rds(team, "prepared_team.rds")

team <- readr::read_rds("prepared_team.rds")
chairs <- team |> 
  dplyr::filter(category == "chairs")

organizers <- team |> 
  dplyr::filter(category == "organizacion")
```

::: {.content-visible when-profile="en"}
# Organizing team 

## About us

On October 25, 2017, an announcement was made by Heather Turner on the R User Group (RUG) Organizer's Slack: the R Foundation Conference Committee was interested in the emergence of academic-focused R events in regions not currently covered by useR! In less than a week, we had organized our first videoconference to start thinking about how to face the challenge. This quick response was not the result of mere luck, but the consequence of a year in which the R community — through its local RUGs and social media presence— grew stronger in South America. By mid November everything was set up: a name, a place, a date, and a motivated international organizing committee. The first edition took place in Buenos Aires, Argentina, in [2018](https://2018.latinr.org/), and the second in Santiago de Chile, Chile, in [2019](https://2019.latinr.org/). We had virtual editions between [2020](https://2020.latinr.org/) and [2022](https://2022.latinr.org/), and in [2023](https://2023.latinr.org/) we met in person in Montevideo, Uruguay. This year the Latin American R community will meet up online again.
:::


::: {.content-visible when-profile="es"}

# Equipo Organizador


## Quiénes somos

El 25 de octubre de 2017, Heather Turner anunció en el Slack de Organizadores de Grupos de Usuarios de R (RUG) que el Comité de Conferencias de la R Foundation estaba interesado en la aparición de eventos sobre R con un enfoque académico en regiones que no se encuentran actualmente cubiertas por useR!. En menos de una semana ya teníamos organizada nuestra primera videoconferencia para pensar cómo enfrentar el desafío. Esta rápida respuesta no fue solo suerte, sino la consecuencia de un año en el que la comunidad de R --a través de los RUGs locales y la presencia en redes sociales-- creció significativamente en Sudamérica. Para mediados de noviembre ya estaba todo definido: un nombre, un lugar, una fecha y un comité organizador internacional motivado. La primera edición se realizó en Buenos Aires, Argentina, en [2018](https://2018.latinr.org/) y la segunda en Santiago de Chile, Chile, en [2019](https://2019.latinr.org/). Luego de las ediciones virtuales entre los años [2020](https://2020.latinr.org/) y [2022](https://2022.latinr.org/), en [2023](https://2023.latinr.org/) la comunidad de R en Latinoamérica se juntó en Montevideo, Uruguay. Para la edición de 2024 regresamos a modalidad virtual.

:::


::: {.content-visible when-profile="pt"}

# Equipe Organizadora

## Sobre nós

Em 25 de outubro de 2017, Heather Turner fez um anúncio no Slack R User Group (RUG) Organizers: o Comitê da Conferência da R Foundation estava interessada na ascensão de eventos sobre R focado na academia nas regiões não cobertas pelo useR! Em menos de uma semana, nós organizamos nossa primeira video conferência para começar a pensar como lidar com este desafio. Esta resposta rápida não foi um resultado de mera sorte, mas a consequência de um ano no qual a comunidada R através de seus RUGs locais e presença em mídias sociais se fortaleceu na América do Sul. Até meados de novembro tudo estava preparado: um nome, um local, uma data e um comitê organizacional internacional motivado. A primeira edição ocorreu em Buenos Aires, Argentina, em [2018](https://2018.latinr.org/), e a segunda em Santiago do Chile, Chile, em [2019](https://2019.latinr.org/). Tivemos edições virtuais entre [2020](https://2020.latinr.org/) e [2022](https://2022.latinr.org/) e, em [2023](https://2023.latinr.org/), voltamos a nos encontrar presencialmente em Montevidéu, Uruguai. Este ano, a comunidade latino-americana de R se reunirá online mais uma vez.

:::


::: {.content-visible when-profile="en"}
### LatinR Chairs
:::

::: {.content-visible when-profile="es"}
### Chairs LatinR
:::

::: {.content-visible when-profile="pt"}
### Presidentes LatinR
:::

```{r}
chairs |>
  dplyr::select(name_complete, titles, icons) |>
  reactable::reactable(
    columns = list(
      name_complete = reactable::colDef(name = "Nombre"), 
      titles = reactable::colDef(name = "Afiliación institucional"), 
      icons = reactable::colDef(name = "Contacto", html = TRUE)  
  )
)
```

::: {.content-visible when-profile="en"}
### Scientific Committee
:::

::: {.content-visible when-profile="pt"}
### Comitê Científico
:::


::: {.content-visible when-profile="es"}
### Comité Científico
:::

Comming soon.

```{r}
# bslib::layout_column_wrap(class = "cards-display",
#   width = 1,
#   gap = "0.5cm",
#   height = 100,
#   purrr::map(committe_list, .f = ~generate_card(.x, class_group = "card-header-comite"))
# )
```



::: {.content-visible when-profile="en"}
### Organizer Committee
:::

::: {.content-visible when-profile="pt"}
### Comitê Organizador
:::


::: {.content-visible when-profile="es"}
### Comité Organizador
:::

```{r}
organizers |>
  dplyr::select(name_complete, titles, icons) |>
  reactable::reactable(
    columns = list(
      name_complete = reactable::colDef(name = "Nombre"), 
      titles = reactable::colDef(name = "Afiliación institucional"), 
      icons = reactable::colDef(name = "Contacto", html = TRUE)  
  )
)
```



<!-- font awesome -->

```{=html}
<script src="https://kit.fontawesome.com/1f72d6921a.js" crossorigin="anonymous"></script>
```
<!-- font awesome -->
